\chapter*{Abstract}
\singlespace
	With ever growing energy demand and system complexity, PMU has become one of the most vital component of the power system. PMU is at the foundation of the control mechanism and hence its accurate and reliable operation is of concern. PMU extends the abilities of power system operate, it enables rapid control and corrective actions and allows for near-limit operations if necessary. This brings in the necessity to standardize the PMU implementation, which brought C37.118, standards in to existence. C37.118 defines minimum necessary performance criteria for device and there by harmonizing the designing and implementation of PMU. Here an effort is made in developing a C37.118 compliant, low-cost PMU. Primary aim of the project was to achieve better reliability and accuracy with as much low cost as possible. Literature survey provided the necessary insight for different aspects of the design. AM3358 based BeagleBone Black running Debian-7.5 is used as platform, around which interfacing circuit for taking inputs is design and GPS module for time reference are connected. Two Programmable Real-time Units (PRU) are used for real-time ADC sampling at 128 samples/cycle and 1PPS detection. A 256 sample moving window based Recursive-DFT algorithm is used for phasor estimation. Frequency, Phase and amplitude after being estimated are time stamped and sent to the PDC via ethernet in standard compliant data frame format. Neon based code vectorization and compiler optimization is also done, via which an impressive performance boost of 1000$\mu$s is achieved. Results and error plots are presented to review the performance of the device.
\doublespace